Shap-based Average Treatment Effect Calculations

### 2019-03-10 Paper/main.tex
Updates from Overleaf

\subsection{Baseline}
Our first method of estimating ATT is Inverse Propensity Score Weighting (IPW).
We use the following equation for calculation of ATT:
\begin{equation*}
    \begin{split}
        ATT = & \mathbb{E}[Y_1 - Y_0 | T=1] \\
        & \mathbb{E}_X[\mathbb{E}[Y_1 - Y_0 | X, T=1]] \\
        & \mathbb{E}_X[\mathbb{E}[Y_1 | X, T=1] - \mathbb{E}[Y_0 | X, T=1]]
    \end{split}
\end{equation*}

@@

\subsection{Simulation}

@@

\end{document}

>>>>

\subsection{Baseline}
Our first method of estimating ATT is Inverse Propensity Score Weighting (IPW).
We use the following equation for calculation of ATT:
\begin{equation*}
    \begin{split}
        ATT = & \mathbb{E}[Y_1 - Y_0 | T=1] \\
        = & \mathbb{E}_X[\mathbb{E}[Y_1 - Y_0 | X, T=1]] \\
        = & \mathbb{E}_X[\mathbb{E}[Y_1 | X, T=1] - \mathbb{E}[Y_0 | X, T=1]]
    \end{split}
\end{equation*}

@@

\subsection{Simulation}
\subsubsection{Kang-Schafer}
Our first method of simulation is the Kang-Schafer method for creating simulated data \cite{kang2007demystifying}. This method assigns four random covariates for every individual ($x_i^j~\mathcal{N}(0,1)$ for every $i\in{}\{1,2,3,4\}$). 
Propensity is then computed in the following way:
\begin{equation*}
    p(T=1| X=x) = \frac{1}{1 + \exp{(x_1 - \frac{x_2}{2} + \frac{x_3}{4} + \frac{x_4}{10})}}
\end{equation*}

We then assign treatment using the true propensity score as the probability for a binomial variable, yielding treatment assignments that are binary.

Given both the covariates and the treatment assignments, we compute a expected outcome as:
\begin{equation*}
    \mathbb{E}[Y|X=x, T=t] = 210 + t + 27.4 \cdot{} x_1 + 13.78 \cdot{} x_2 + 13.7 \cdot{} x_3 + 13.7 \cdot{} x_4
\end{equation*}

Under the strong ignorability assumption and equations from the Kang-Schafer paper we can compute the true ATT using the following steps:
\begin{equation*}
    \begin{split}
        ATT = & \mathbb{E}[Y_1 | X=x, T=1] - \mathbb{E}[Y_0 | X=x, T=1] \\
        \mathbb{E}[Y_1|T=1, X=x] = & \mathbb{E}[Y|T=1, X=x] \\
        \mathbb{E}[Y_0|T=1, X=x] = & \mathbb{E}[Y_0|T=0, X=x] = \mathbb{E}[Y|T=0, X=x] \\
    \end{split}
\end{equation*}
Therefore $ATT=\mu{}^{(1)} - \mu{}^{(0)} = 200-220 = -20$ 
%TODO: is this not actually 20?

\subsubsection{Z-Bias}

@@

\end{document}Y1Y1
